---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SumStat

<!-- badges: start -->
<!-- badges: end -->

The purpose of SumStat is to provide convenient tools for users to calcaulte the summary of statistics of a given dataset.   

Use `SumStat` to:     
- calculate the coefficient of variation of given data      
- calculate the range of given data 

## Installation

You can install the pre-released version of `SumStat` with:

``` r
devtools::install_github("Ella-Q/SumStat")
```

## Example

This is a basic example which shows you how to work with functions in `SumStat`:

```{r example}
library(SumStat)

# calculate the coefficient of variation 
CVar(c(5:10, NA), remove_na = T)
```

## Steps in developing the R package
1. load the `devtools` package in a console, and then run `create_package("SumStat)` in the console    
2. In the newly-opened R project named SumStat, reload the `devtools` package and run `use_git()`    
3. Run `use_r("CVar")` and `use_r("range")` to open R scripts
4. After writing the functions in R scripts, run `load_all()`
5. Run `check()`
6. Run `use_mit_license("Qing Qiu")` to edit the license in the DESCRIPTION file   
7. Click on the each function in the R scripts, and do Code --> Insert roxygen skeleton to document each function. Then, run `document()` in the console
8. Run `use_readme_rmd()` to add a README file and render it with `build_readme()`
9. Make a vignette with `use_vignette("range")`   
10. Run `use_testthat()` to include tests in the package   
